Online Verification of Commutativity

### 2020-08-13 acmPaper/paper.tex
Bib fixes
Added section on Gator

\newcount\draft\draft=1 % set to 0 for submission or publication
\documentclass[sigplan,review,anonymous]{acmart}
\setcopyright{none}
%
\usepackage{tikz}
\usetikzlibrary{snakes}
\usepackage[norelsize]{algorithm2e}
\usepackage{xxx}
\usepackage{fncylab}
\usepackage{subcaption}
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

@@

@@

@@

\xxx{Write the Gator section!}

@@

To demonstrate our algorithms applied to a real world situation,
we found inconsistencies in a diagram of the exchange rate between currencies.
Consider a diagram with nodes as currencies and a directed edge being the
conversion rate from its source node's currency to its sink node's currency.
Since the transformation exchange rate of money from any given base currency to a target currency
can be expected to be the same regardless of which intermediate currency transformations
are used, this diagram should commute.

@@

\section{Conclusion}

>>>>

\newcount\draft\draft=1 % set to 0 for submission or publication
\documentclass[sigplan,review,anonymous]{acmart}
\setcopyright{none}
%
\usepackage{tikz}
\usetikzlibrary{snakes}
\usepackage[norelsize]{algorithm2e}
\usepackage{xxx}
\usepackage{fncylab}
\usepackage{subcaption}
\usepackage{listings}
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

@@

\newcommand{\code}{\lstinline[keywordstyle=]}

@@

To demonstrate our algorithms applied to a real world situation,
we search for inconsistencies in diagrams of geometry transformations, and in a diagram of the exchange rate between currencies.

@@

Gator is a domain specific language designed around Geometry types, which are used to describe properties and transformations of geometric objects.  A key feature of Gator is \code{in} expressions, which insert code to automatically transform between two geometry types.  For example, given a point \code{p} represented in 2-dimensional Cartesian coordinates (which has type \code{cart2}), we can transform this point into polar coordinates using the expression \code{p in polar}.

A key property of these \code{in} expressions is that the path chosen between two representations is arbitrary; thus we would like to ensure that every path is equivalent.  This problem defines a natural application space for working with our commutative diagrams, so long as we can define a transformation graph and oracle.

For simplicity, and to stay in scope for this paper, we focus on geometry transformations between \textit{reference frames}, which are the geometry equivalent of transforming between linear algebra basis vectors.  Each edge on our transformation graph is a thus a matrix, with composition of edges as matrix multiplication and an oracle checking matrix equality (up to a rounding error $\epsilon$).

These sorts of transformations are very common in graphics programming, and there are several examples of reasonably complicated transformation graphs that we can pick from.  Gator includes several graphics examples as part of its examples package; for this evaluation, we looked at the \textit{phong}, \textit{reflection}, and \textit{shadow map} examples, sample images of which can be seen in Appendix~\ref{sec:gator-appendix}.

We implemented a system for interfacing with the optimal set incremental checker in Gator \xxx[dg]{Which algorithm was it?}.  Gator uses TypeScript for CPU computations, so it was reasonable to build a system to manage graphs for interoperation with the path independence algorithm.

Using this algorithm, we found a bug in the reflection model, where a matrix was not being divided correctly by its determinant \xxx[dg]{List other things I find, if anything}.  We also inserted previous bugs to check the algorithm was working correctly, and it identified all inserted bugs.

@@

Consider a diagram with nodes as currencies and a directed edge being the
conversion rate from its source node's currency to its sink node's currency.
Since the transformation exchange rate of money from any given base currency to a target currency
can be expected to be the same regardless of which intermediate currency transformations
are used, this diagram should commute.

@@

\section{Example Gator Images}
\label{sec:gator-appendix}
\begin{figure}
	\begin{subfigure}{\linewidth}
		\includegraphics[width=\linewidth]{phong.png}
		\caption{Phong Lighting Model}
	\end{subfigure}

	\begin{subfigure}{\linewidth}
		\includegraphics[width=\linewidth]{reflection.png}
		\caption{Reflection Model}
	\end{subfigure}

	\begin{subfigure}{\linewidth}
		\includegraphics[width=\linewidth]{shadowmap.png}
		\caption{Shadow Map Model}
	\end{subfigure}

	\caption{Example Images from Gator Programs}
	\label{fig:gator-images}
\end{figure}
